---
title: "Redclaw AES Supporting Material"
author: "Vinny"
date: "2022-11-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r libraries}
# import libraries
library(tidyverse)
library(broom)
library(kableExtra)
```

```{r initial_mass}
# define parameters
bw_0 <- 0.0221
```

## Deliverables:

* Develop growth model
* Develop production plan
* Perform system mass balance equations
* Develop prototype system

***

## Growth Modeling:

Literature review undertaken to provide growth data for as wide a range of life-stage. This data collection does not replace the benefit of a formal growth trial undertaken under replication of proposed production specifications.


**_Cherax quadricarinatus_** growth characteristics:

``` {r growth_rate, fig.cap = "Figure 1. Daily growth rate by mass - datapoints from published literature.", fig.align = "center"}
# import data
redclaw_growth <- read.csv("data/redclaw_growth.csv")

redclaw.growth <- redclaw_growth %>%
  mutate(wt.mid = (wt_2 + wt_1) / 2,
         g.gain.day = (wt_2 - wt_1) / (t_2 - t_1),
         geometric.weight = sqrt(wt_1 * wt_2))

# try base code log-log relationship - looks good!
redclaw.fit.twinlog <- lm(log(g.gain.day) ~ log(wt.mid), data = redclaw.growth)

# calculate coefficients for growth curve bw_1 = [bw_0^c_1 + c_2 * days]^c_4
c_1 <- 1 - redclaw.fit.twinlog$coef[2]
c_2 <- c_1 * exp(redclaw.fit.twinlog$coef[1])
c_4 <- 1 / c_1

# plot relationship between weight and grams gained per day 
p_rc_gain <- redclaw.growth %>%
  ggplot(aes(wt.mid, g.gain.day, color = source)) +
  geom_point() +
  stat_function(fun = function(x) exp(redclaw.fit.twinlog$coef[1]) * x^redclaw.fit.twinlog$coef[2], color = 'dodgerblue') +
  xlab("Mass (g)") +
  ylab("Daily mass gain (g/cray/day)") +
  theme_minimal()

p_rc_gain
```

***
From the growth model, an estimate of crayfish body mass - as a function of time from hatch - can be calculated

```{r crayfish_mass, fig.cap = "Figure 2. Estimated crayfish mass at time from hatch.", fig.align='center'}
# estimate body-weight over time geometric model
bodyweight <- tibble(day = seq(1,300,1)) %>%
  mutate(bw = (bw_0^c_1 + c_2 * day)^c_4)

# plot estimated growth curve geometric
cray.growth.plot <- bodyweight %>%
  ggplot(aes(day, bw)) +
  geom_line() +
  labs(x = "Days", y = "Mass (g)") +
  theme_minimal()
cray.growth.plot
```

```{r harvest_days}
cray.max <- 1
juvenile.25 <- 25
juvenile.max <- 45
crayling.1.g <- ceiling(which(abs(bodyweight$bw - cray.max) == min(abs(bodyweight$bw - cray.max))))
juvenile.25.g <- ceiling(which(abs(bodyweight$bw - 25) == min(abs(bodyweight$bw - 25))))
juvenile.45.g <- ceiling(which(abs(bodyweight$bw - juvenile.max) == min(abs(bodyweight$bw - juvenile.max))))
crayling.harvest.day <- 7 * ceiling(which(abs(bodyweight$bw - cray.max) == min(abs(bodyweight$bw - cray.max))) / 7)
juvenile.harvest.day <- 7 * ceiling(which(abs(bodyweight$bw - juvenile.max) == min(abs(bodyweight$bw - juvenile.max))) / 7)
```


Estimated growth day for `r cray.max`g craylings: Day `r crayling.1.g`
Estimated growth day for `r juvenile.25`g juveniles: Day `r juvenile.25.g`
Estimated growth day for `r juvenile.max`g juveniles: Day `r juvenile.45.g`

***

## Production Plan

```{r crayling_parameters}
crayling.monthly.target <- 227000 # monthly target of crayling stage 2 (min six weeks)
breeding.population <- 5200
fecundity <- 400 # number of eggs produced
hatch.rate <- 0.9
crayling.survival <- 0.7 # proportion survival from egg to stage 2
hatching.frequency <- 3 # number of spawning events per year
breeding.females <- breeding.population / 3 * 2
breeding.males <- breeding.females / 2
weekly.egg.prod <- breeding.females * 400 * 3 / 365 * 7
weekly.egg.hatch <- weekly.egg.prod * hatch.rate
cray.daily.mortality <- 0.00625
breeding.population <- 5200
average.adult.mass <- 100
uk.breeding.population <- breeding.population / 225
uk.breeding.females <- uk.breeding.population * 2 / 3
uk.weekly.egg.prod <- uk.breeding.females * 400 * 3 / 365 * 7
uk.weekly.egg.hatch <- uk.weekly.egg.prod * hatch.rate
harvest.proportion <- 0.99
```

Develop production plan(s) to achieve:

* UK redclaw start-up hub, maximise production permitted by available space
* Redclaw commercial scale, monthly target `r format(crayling.monthly.target, scientific = FALSE)` (moult stage-2) `r cray.max`g craylings for harvest
* UK breeding pairs as dictated by space
* Commercial breeding pairs `r breeding.population`

Parameters used:

* Average fecundity `r fecundity`
* Hatch rate `r hatch.rate * 100`%
* Survival rate from egg to stage-2 moult crayling `r crayling.survival * 100`%
* Breeding cycles; `r hatching.frequency` per year

System designation:

* Breeding - maintain breeding population of `r breeding.population` adult crayfish
* Hatching - maintain berried crayfish in isolation until egg hatch
* Crayling - maintain hatchlings until `r cray.max`g (stage-2 moult)
* Juvenile - maintain retained juvenile crayfish until `r juvenile.max`g

```{r prod_plan}
# import data
redclaw.feed_rate <- read.csv("data/redclaw_feed_rate.csv")

# try base code log-log relationship - looks good!
redclaw.feed.twinlog <- lm(log(feed_rate) ~ log(mass), data = redclaw.feed_rate)

batch_frequency <- 7 # days between batches
batch_system_periods <- 1 # overall number of system periods
growout_period <- 350 # period whose factor includes frequency, system period and exceeds minimum growout period

# set production period to two growth periods to observe system loading
prod_plan <- data.frame(facility_day = seq(0, 2 * growout_period - 1)) %>%
  mutate(batch_1 = case_when(facility_day < growout_period ~ facility_day))

for (lag_size in c(0:40)) {
  
  new_col_name <- paste0("lag.batch.", lag_size)
  
  prod_plan <- prod_plan %>%
    mutate(!!sym(new_col_name) := lag(batch_1, n = lag_size * 7, default = NA))
}  

# remove column called batch_1
prod_plan <- prod_plan %>% select(-batch_1) %>%
  pivot_longer(c(lag.batch.0:lag.batch.40), names_to = "batch", values_to = "batch_day", values_drop_na = TRUE) %>%
  mutate(system = case_when(batch_day %in% c(0:crayling.harvest.day) ~ "crayling",
                            batch_day %in% c(crayling.harvest.day + 1 :juvenile.harvest.day - crayling.harvest.day) ~ "juvenile",
                            batch_day > juvenile.harvest.day ~ "breeding"))

prod.plan.1 <- prod_plan %>%
  filter(system == "crayling" | system == "juvenile" | system == "breeding" & batch == "lag.batch.0")


# custom color
system_cols <- c(crayling = "#e5f5f9", juvenile = "99d8c9", breeding = "2ca25f")
```

***

```{r prod_plan_plot, fig.cap = "Figure 3. Production plan visualisation.", fig.align = "center"}
systems_plot <- prod.plan.1 %>%
  filter(facility_day < 328,
         batch %in% c('lag.batch.0', 'lag.batch.1', 'lag.batch.2', 'lag.batch.3', 'lag.batch.4', 'lag.batch.5', 'lag.batch.6', 'lag.batch.7', 'lag.batch.8', 'lag.batch.9', 'lag.batch.10', 'lag.batch.11', 'lag.batch.12', 'lag.batch.13')) %>%
  ggplot(aes(facility_day, batch, color = system)) +
  geom_line(size = 3) +
  scale_y_discrete(limits = c('lag.batch.0', 'lag.batch.1', 'lag.batch.2', 'lag.batch.3', 'lag.batch.4', 'lag.batch.5', 'lag.batch.6', 'lag.batch.7', 'lag.batch.8', 'lag.batch.9', 'lag.batch.10', 'lag.batch.11', 'lag.batch.12', 'lag.batch.13'),
                   labels = c("Batch 1", "Batch 2", "Batch 3", "Batch 4", "Batch 5", "Batch 6", "Batch 7", "Batch 8", "Batch 9", "Batch 10", "Batch 11", "Batch 12", "Batch 13", "Batch 14")) +
  scale_color_manual("", breaks = c("crayling", "juvenile", "breeding"),
                     values = c(crayling = "#a6cee3", juvenile = "#1f78b4", breeding = "#b2df8a"),
                     labels = c("Crayling", "Juvenile", "Breeding")) +
  labs(x = "Day", y = "") + 
  theme_minimal()
systems_plot
```

Estimated harvest day for `r cray.max`g craylings: Day `r crayling.harvest.day`
Estimated growth day for `r juvenile.max`g juveniles: Day `r juvenile.harvest.day`

***

## System Occupancy

System occupancy will be use to determine tank space and tank divisions, split according to:

* UK System
* Production Facility

``` {r system_occupancy}
system_loading <- prod.plan.1 %>%
  mutate(cray.number = weekly.egg.hatch * (1 - cray.daily.mortality)^batch_day,
         cray.number.mod = case_when(system == "juvenile" ~ weekly.egg.hatch * (1 - cray.daily.mortality)^crayling.harvest.day * (1 - harvest.proportion) * (1 - cray.daily.mortality)^(batch_day - crayling.harvest.day),
                                     system == "crayling" ~ weekly.egg.hatch * (1 - cray.daily.mortality)^batch_day,
                                     system == "breeding" ~ breeding.population),
         cray.number.mod.2 = case_when(system == "juvenile" ~ weekly.egg.hatch * (1 - cray.daily.mortality)^crayling.harvest.day * (1 - harvest.proportion) * (1 - cray.daily.mortality)^(batch_day - crayling.harvest.day),
                                       system == "crayling" ~ weekly.egg.hatch * (1 - cray.daily.mortality)^crayling.1.g,
                                       system == "breeding" ~ breeding.population),
         bw.g = case_when(system == "crayling" ~ (bw_0^c_1 + c_2 * batch_day)^c_4,
                          system == "juvenile" ~ (bw_0^c_1 + c_2 * batch_day)^c_4,
                          system == "breeding" ~ average.adult.mass),
         unit = breeding.population * 2 / 3 * 3 / 365, # expected number of hatches per day
         total.bw = bw.g * cray.number.mod,
         feed.rate = case_when(exp(redclaw.feed.twinlog$coef[1]) * bw.g^redclaw.feed.twinlog$coef[2] >= 0.01 ~ exp(redclaw.feed.twinlog$coef[1]) * bw.g^redclaw.feed.twinlog$coef[2], TRUE ~ 0.01),
         feed.g = bw.g * feed.rate,
         total.feed.kg = feed.g * cray.number.mod / 1000,
         protein.proportion = case_when(bw.g < 5 ~ 0.325, TRUE ~ 0.256),
         total.protein = protein.proportion * total.feed.kg)

# calculate max number of individuals in system at any one time
max.occupancy <- system_loading %>%
  group_by(system, facility_day) %>%
  summarise(t_number = sum(cray.number.mod)) %>%
  summarise(max.number = max(t_number))

# calculate max number of units in system at any one time
unit.number <- system_loading %>%
  group_by(system, batch) %>%
  summarise(unit.sum = sum(unit)) %>%
  summarise(max.unit = max(unit.sum))

# get max loading for each system
max.loading <- system_loading %>%
  group_by(system, facility_day) %>%
  summarise(feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein),
            t_number = sum(cray.number.mod),
            mod.number = sum(cray.number.mod.2)) %>%
  summarise(feed.max = max(feed.sum),
            protein.max = max(protein.sum),
            max.number = max(t_number),
            max.mod.number = max(mod.number))

grouped.loading <- max.loading %>%
  add_row(system = "breeding.juvenile",
          feed.max = max.loading$feed.max[1] - max.loading$feed.max[1] * 24 / 52 * 2 / 3 + max.loading$feed.max[3],
          protein.max = max.loading$protein.max[1] - max.loading$protein.max[1] * 24 / 52 * 2 / 3 + max.loading$protein.max[3]) %>%
  add_row(system = "crayling.hatching",
          feed.max = max.loading$feed.max[1] * 24 / 52 * 2 / 3 + max.loading$feed.max[2],
          protein.max = max.loading$protein.max[1] * 24 / 52 * 2 / 3 + max.loading$protein.max[2]) %>%
  filter(system %in% c("breeding.juvenile", "crayling.hatching"))
```


```{r}
# build uk system loading onto production plan
uk.system_loading <- prod.plan.1 %>%
  mutate(cray.number = uk.weekly.egg.hatch * (1 - cray.daily.mortality)^batch_day,
         cray.number.mod = case_when(system == "juvenile" ~ uk.weekly.egg.hatch * (1 - cray.daily.mortality)^crayling.harvest.day * 0.01 * (1 - cray.daily.mortality)^(batch_day - crayling.harvest.day),
                                     system == "crayling" ~ uk.weekly.egg.hatch * (1 - cray.daily.mortality)^batch_day,
                                     system == "breeding" ~ uk.breeding.population),
         cray.number.mod.2 = case_when(system == "juvenile" ~ uk.weekly.egg.hatch * (1 - cray.daily.mortality)^crayling.harvest.day * (1 - harvest.proportion) * (1 - cray.daily.mortality)^(batch_day - crayling.harvest.day),
                                       system == "crayling" ~ uk.weekly.egg.hatch * (1 - cray.daily.mortality)^crayling.1.g,
                                       system == "breeding" ~ uk.breeding.population),
         bw.g = case_when(system == "crayling" ~ (bw_0^c_1 + c_2 * batch_day)^c_4,
                          system == "juvenile" ~ (bw_0^c_1 + c_2 * batch_day)^c_4,
                          system == "breeding" ~ 100),
         unit = uk.breeding.population * 2 / 3 * 3 / 365, # expected number of hatches per day
         total.bw = bw.g * cray.number.mod,
         feed.rate = case_when(exp(redclaw.feed.twinlog$coef[1]) * bw.g^redclaw.feed.twinlog$coef[2] >= 0.01 ~ exp(redclaw.feed.twinlog$coef[1]) * bw.g^redclaw.feed.twinlog$coef[2], TRUE ~ 0.01),
         feed.g = bw.g * feed.rate,
         total.feed.kg = feed.g * cray.number.mod / 1000,
         protein.proportion = case_when(bw.g < 5 ~ 0.325, TRUE ~ 0.256),
         total.protein = protein.proportion * total.feed.kg)

# calculate max number of individuals in system at any one time
uk.max.occupancy <- uk.system_loading %>%
  group_by(system, facility_day) %>%
  summarise(t_number = sum(cray.number.mod)) %>%
  summarise(max.number = max(t_number))

# calculate max number of units in system at any one time
uk.unit.number <- uk.system_loading %>%
  group_by(system, batch) %>%
  summarise(unit.sum = sum(unit)) %>%
  summarise(max.unit = max(unit.sum))

# get max loading for each system
uk.max.loading <- uk.system_loading %>%
  group_by(system, facility_day) %>%
  summarise(feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein),
            t_number = sum(cray.number.mod),
            mod.number = sum(cray.number.mod.2)) %>%
  summarise(feed.max = max(feed.sum),
            protein.max = max(protein.sum),
            max.number = max(t_number),
            max.mod.number = max(mod.number))

uk.grouped.loading <- uk.max.loading %>%
  add_row(system = "breeding.juvenile",
          feed.max = uk.max.loading$feed.max[1] - uk.max.loading$feed.max[1] * 24 / 52 * 2 / 3 + uk.max.loading$feed.max[3],
          protein.max = uk.max.loading$protein.max[1] - uk.max.loading$protein.max[1] * 24 / 52 * 2 / 3 + uk.max.loading$protein.max[3]) %>%
  add_row(system = "crayling.hatching",
          feed.max = uk.max.loading$feed.max[1] * 24 / 52 * 2 / 3 + uk.max.loading$feed.max[2],
          protein.max = uk.max.loading$protein.max[1] * 24 / 52 * 2 / 3 + uk.max.loading$protein.max[2]) %>%
  filter(system %in% c("breeding.juvenile", "crayling.hatching"))
```

```{r}
knitr::kables(
  list(
    # the first kable() to change column names
    knitr::kable(
      max.occupancy, col.names = c("Production System   | ", " Max Number"), valign = 't', digits = 0,
    ),
    # the second kable() to set the digits option
    knitr::kable(uk.max.occupancy, digits = 0, col.names = c("UK System   | ", " Max Number") ,valign = 't')
  ),
  caption = 'Table 1. Production facility; system occupation.'
) %>% kable_styling()
```


```{r}
knitr::kables(
  list(
    # the first kable() to change column names
    unit.number %>% filter(system == "crayling") %>% knitr::kable(
      col.names = c("Production System   | ", " Max Number"), valign = 't', digits = 0,
    ),
    # the second kable() to set the digits option
    uk.unit.number %>% filter(system == "crayling") %>% knitr::kable(digits = 0, col.names = c("UK System   | ", " Max Number") ,valign = 't')
  ),
  caption = "Table 2. Production facility; number of individual crayling 'families'."
) %>% kable_styling()
```


***

## Space Requirements

```{r}
# build production tanks
flow.contingency <- 1.0 # extra flow capacity for system
breeding.density <- 7
hatching.density <- 20
crayling.density <- 250
juvenile.density <- 19
tank.areas <- tibble(system = c("breeding", "hatching", "crayling", "juvenile"),
                     ind.number = c(max.loading$max.mod.number[1], max.loading$max.mod.number[1] * 24 / 52 * 2 / 3, max.loading$max.mod.number[2], max.loading$max.mod.number[3]),
                     area.required = ind.number / c(7, 20, 250, 19),
                     water.depth = c(0.15, 0.15, 0.15, 0.15),
                     tank.volumes = area.required * water.depth,
                     tank.turnover = tank.volumes * flow.contingency)

# build UK tanks
uk.tank.areas <- tibble(system = c("breeding", "hatching", "crayling", "juvenile"),
                     ind.number = c(uk.max.loading$max.mod.number[1], uk.max.loading$max.mod.number[1] * 24 / 52 * 2 / 3, uk.max.loading$max.mod.number[2], uk.max.loading$max.mod.number[3]),
                     area.required = ind.number / c(breeding.density, hatching.density, crayling.density, juvenile.density),
                     water.depth = c(0.15, 0.15, 0.15, 0.15),
                     tank.volumes = area.required * water.depth,
                     tank.turnover = tank.volumes * flow.contingency)
```

Space allocation according to the following densities per sq. metre

* Breeding; `r breeding.density`
* Hatching; `r hatching.density`
* Crayling; `r crayling.density`
* Juvenile; `r juvenile.density`

``` {r}
knitr::kable(tank.areas, digits = 2, caption = "Table 3. Production facility tank area requirements (sq. metres), volumes (cubic metres).", col.names = c("System", "Capacity", "Area", "Water Depth", "Tank Volumes ", "Tank Turnover")) %>%
  kable_styling()
```


``` {r}
knitr::kable(uk.tank.areas, digits = 2, caption = "Table 4. UK facility tank area requirements (sq. metres), volumes (cubic metres).", col.names = c("System", "Capacity", "Area", "Water Depth", "Tank Volumes ", "Tank Turnover")) %>%
  kable_styling()
```

``` {r single_batch}

# single batch calculations

single.batch <- tibble(system = c("breeding", "hatching", "crayling", "juvenile"),
                       ind.number = c(3, 1, fecundity * hatch.rate * (1 - cray.daily.mortality)^crayling.harvest.day, fecundity * hatch.rate * (1 - cray.daily.mortality)^crayling.harvest.day * 0.01),
                       area.required = ind.number / c(breeding.density, hatching.density, crayling.density, juvenile.density),
                       water.depth = c(0.15, 0.15, 0.15, 0.15),
                       tank.volumes = area.required * water.depth,
                       tank.turnover = tank.volumes * flow.contingency)

```

``` {r single_batch_table}

knitr::kable(single.batch, digits = 2, caption = "Table 5. Single batch tank area requirements (sq. metres), volumes (cubic metres).", col.names = c("System", "Capacity", "Area", "Water Depth", "Tank Volumes ", "Tank Turnover")) %>%
  kable_styling()
```


***

## Water Quality

``` {r}
# define water quality parameters
desired.tss <- 20 # max 20 mg/l in tanks
desired.o2 <- 5.0 # min 5 mg/l in tanks
desired.tan <- 1 # max 1 mg/l TAN in tanks
desired.nitrate <- 50 # max 50 mg/l nitrate in tanks
desired.co2 <- 15 # max 15 mg/l in tanks
desired.t <- 28 # system operating temp in C
site.altitude <- 50 # site altitude in metres
cone.bar <- 0.7
feeding.period <- 12
metabolic.period <- feeding.period + 4
```

The following parameters have been used to build system water treatment requirements:

* **TSS** - maximum `r desired.tss` mg/l in livestock tanks
* **Oxygen** - minimum `r desired.o2` mg/l in livestock tanks
* **TAN** - maximum `r desired.tan` mg/l in livestock tanks
* **Nitrate** - `r desired.nitrate` mg/l accumulation in system
* **CO~2~** - maximum `r desired.co2` mg/l in livestock tanks
* **Temperature** - maintain `r desired.t` $^\circ$C in system
* **Altitude** - `r site.altitude` m above sea level
* **Feeding period** - active feeding period of `r feeding.period` hours
* **Metabolic period** - active metabolic period of `r metabolic.period` hours

``` {r}
# constants
k <- 1.42903
beta.oxygen <- exp(-58.3877 + 85.8079 *  (100/(desired.t + 273.15)) + 23.8439 * log((desired.t+273.15) / 100))
barometric.pressure <- 10^(2.88014 - site.altitude/19748.2)
water.v.pressure <- 4.7603 * exp(0.0645 * desired.t)
oxygen.percent <- 20.95
oxygen.saturation <- 1000 * k * beta.oxygen * oxygen.percent / 100 * ((barometric.pressure - water.v.pressure) / 760) # if cone used at pressure swap out barometric.pressure for cone.pressure
cone.pressure <- cone.bar * 750.06 + barometric.pressure

# component specifics
# system efficiency 
tan.c1 <- desired.tan
tan.cbest <- 0
tan.te <- 0.9
tan.c2 <- tan.c1 + tan.te * (tan.cbest - tan.c1)

co2.c1 <- desired.co2
co2.cbest <- 0.5
co2.te <- 0.7
co2.c2 <- co2.c1 + co2.te * (co2.cbest - co2.c1)

tss.c1 <- desired.tss
tss.cbest <- 0
tss.te <- 0.70
tss.c2 <- tss.c1 + tss.te * (tss.cbest - tss.c1)

oxy.c1 <- desired.o2 # min 5 mg/l in tanks
oxy.cbest <- oxygen.saturation
oxy.te <- 0.99
oxy.c2 <- oxy.c1 + oxy.te * (oxy.cbest - oxy.c1)
```

``` {r}
# parameter production
system.parameters <- grouped.loading %>%
  mutate(p.tan = protein.max * 0.092,
         tss = feed.max * 0.25,
         total.od = feed.max * 0.5,
         fish.het.od = feed.max * 0.37,
         nitrif.od = feed.max * 0.13,
         feed.co2 = 0.37 * feed.max * 1.375)

# uk parameter production
uk.system.parameters <- uk.grouped.loading %>%
  mutate(p.tan = protein.max * 0.092,
         tss = feed.max * 0.25,
         total.od = feed.max * 0.5,
         fish.het.od = feed.max * 0.37,
         nitrif.od = feed.max * 0.13,
         feed.co2 = 0.37 * feed.max * 1.375)
```

```{r}
system.flows <- system.parameters %>%
  mutate(tan.flow = abs(p.tan * 1e6 / (tan.c2 - tan.c1) / metabolic.period / 1000),
         co2.flow = abs(feed.co2 * 1e6 / (co2.c2 - co2.c1) / 24 / 1000),
         tss.flow = abs(tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         oxy.flow = abs(fish.het.od * 1e6 / (oxy.c2 - oxy.c1) / 24 / 1000)) %>%
  select(c(system, tan.flow, co2.flow, tss.flow, oxy.flow))

uk.system.flows <- uk.system.parameters %>%
  mutate(tan.flow = abs(p.tan * 1e6 / (tan.c2 - tan.c1) / metabolic.period / 1000),
         co2.flow = abs(feed.co2 * 1e6 / (co2.c2 - co2.c1) / 24 / 1000),
         tss.flow = abs(tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         oxy.flow = abs(fish.het.od * 1e6 / (oxy.c2 - oxy.c1) / 24 / 1000)) %>%
  select(c(system, tan.flow, co2.flow, tss.flow, oxy.flow))
```

``` {r system_flows}
knitr::kable(system.flows, digits = 3, caption = "Table 6. Minimum required flow (m^3^/h) through tanks to maintain desired system parameters in **prodution** facility.", col.names = c("System", "TAN Flow", "C0~2~ Flow", "TSS Flow", "O~2~ Flow")) %>%
  kable_styling()
```

``` {r uk_system_flows}
knitr::kable(uk.system.flows, digits = 3, caption = "Table 7. Minimum required flow (m^3^/h) through tanks to maintain desired system parameters in **UK** facility.", col.names = c("System", "TAN Flow", "C0~2~ Flow", "TSS Flow", "O~2~ Flow")) %>%
  kable_styling()
```

Defining Breeding / Juvenile **Production** system turnover rate: `r format(max(c(system.flows$tan.flow[1], system.flows$co2.flow[1], system.flows$tss.flow[1], system.flows$oxy.flow[1], tank.areas$tank.turnover[1] + tank.areas$tank.turnover[4])), digits = 3)`m^3^/h

Defining Crayling / Hatching **Production** system turnover rate: `r format(max(c(system.flows$tan.flow[2], system.flows$co2.flow[2], system.flows$tss.flow[2], system.flows$oxy.flow[2], tank.areas$tank.turnover[2] + tank.areas$tank.turnover[3])), digits = 3)`m^3^/h

Defining Breeding / Juvenile **UK** system turnover rate: `r format(max(c(uk.system.flows$tan.flow[1], uk.system.flows$co2.flow[1], uk.system.flows$tss.flow[1], uk.system.flows$oxy.flow[1], uk.tank.areas$tank.turnover[1] + uk.tank.areas$tank.turnover[4])), digits = 3)`m^3^/h

Defining Crayling / Hatching **UK** system turnover rate: `r format(max(c(uk.system.flows$tan.flow[2], uk.system.flows$co2.flow[2], uk.system.flows$tss.flow[2], uk.system.flows$oxy.flow[2], uk.tank.areas$tank.turnover[2] + uk.tank.areas$tank.turnover[3])), digits = 3)`m^3^/h

***

## Nitrogen

``` {r nitrogen_parameters}
# component specifics
media.area <- 750 # 750 m2/m3
biomedia.volume.ratio <- 2
biomedia.aeration.ratio <- 3

# system rates
nitrification.rate <- 0.4 # 0.4g TAN/m2/day
skimmer.ratio <- 0.3

# system efficiency 
passive.nitrification <- 0.05 # 5% passive nitrification rate
passive.denitrification <- 0.05 # 5% passive denitrification rate
```

``` {r prod_biofilter}
# uk biofilter
biofilter.max <- grouped.loading %>%
  mutate(tan.max = protein.max * 0.092,
         nitrate.exchange = tan.max * 1e6 * (1 - passive.denitrification) / desired.nitrate / 1000, # exchange volume m3 to maintain nitrate levels 
         available.tan = tan.max * (1 - passive.nitrification) - (desired.tan / 1e6) * nitrate.exchange * 1000, # available tan after passive denitrification and water exchange
         biofilter.exchange = abs(available.tan  * 1e6 / (tan.c2 - tan.c1) / metabolic.period / 1000),
         biomedia.volume = available.tan / (nitrification.rate / 1000) / metabolic.period * 24 / media.area, # biomedia volume required m3
         biofilter.volume = biomedia.volume * biomedia.volume.ratio,
         biofilter.aeration = biomedia.aeration.ratio * biomedia.volume)
```

Section focus on:

* Nitrogenous compounds
* Bio-filter specification
* De-gas requirements
* Protein skimmer requirements

``` {r prod_nitrogen}
biofilter.max %>% select(-c(max.number, max.mod.number)) %>% knitr::kable( digits = 3, caption = "Table 8. **Production** facility bio-filter maximum loading and specification.", col.names = c("System", "Feed Kg", "Protein Kg", "TAN kg", "Exchange m^3^", "Available TAN Kg", "Flow m^3^", "Biomedia m^3^", "Biofilter m^3^", "Aeration m^3^")) %>%
  kable_styling()
```

``` {r uk_biofilter}
# build uk system
uk.biofilter.max <- uk.grouped.loading %>%
  select(-c(max.number, max.mod.number)) %>%
  mutate(tan.max = protein.max * 0.092,
         nitrate.exchange = tan.max * 1e6 * (1 - passive.denitrification) / desired.nitrate / 1000, # exchange volume m3 to maintain nitrate levels 
         available.tan = tan.max * (1 - passive.nitrification) - (desired.tan / 1e6) * nitrate.exchange * 1000, # available tan after passive denitrification and water exchange
         biofilter.exchange = abs(available.tan  * 1e6 / (tan.c2 - tan.c1) / metabolic.period / 1000),
         biomedia.volume = available.tan / (nitrification.rate / 1000) / metabolic.period * 24 / media.area, # biomedia volume required m3
         biofilter.volume = biomedia.volume * biomedia.volume.ratio,
         biofilter.aeration = biomedia.aeration.ratio * biomedia.volume)
```


``` {r uk_nitrogen}
uk.biofilter.max %>% knitr::kable( digits = 3, caption = "Table 9. **UK** facility bio-filter maximum loading and specification.", col.names = c("System", "Feed Kg", "Protein Kg", "TAN kg", "Exchange m^3^", "Available TAN Kg", "Flow m^3^", "Biomedia m^3^", "Biofilter m^3^", "Aeration m^3^")) %>%
  kable_styling()
```

``` {r prod_degas}
degass.calculations <- grouped.loading %>%
  select(-c(max.number, max.mod.number)) %>%
  mutate(tank.turnover = c(tank.areas$tank.turnover[1] + tank.areas$tank.turnover[4], tank.areas$tank.turnover[2] + tank.areas$tank.turnover[3]),
         skimmer.flow = tank.turnover * skimmer.ratio,
         alkalinity.required = feed.max * 0.15,
         naoh.required = alkalinity.required / 1.25,
         co2.remaining = (feed.max * 0.5 - (naoh.required / 1.82)) * 0.9 * 0.5,
         degass.flowrate = biofilter.max$nitrate.exchange * (co2.cbest - co2.c1) + abs(co2.remaining * 1e6 / (co2.c2 - co2.c1)) / 24 / 1000)
```

``` {r uk_degas}
uk.degass.calculations <- uk.grouped.loading %>%
  select(-c(max.number, max.mod.number)) %>%
  mutate(tank.turnover = c(uk.tank.areas$tank.turnover[1] + uk.tank.areas$tank.turnover[4], uk.tank.areas$tank.turnover[2] + uk.tank.areas$tank.turnover[3]),
         skimmer.flow = tank.turnover * skimmer.ratio,
         alkalinity.required = feed.max * 0.15,
         naoh.required = alkalinity.required / 1.25,
         co2.remaining = (feed.max * 0.5 - (naoh.required / 1.82)) * 0.9 * 0.5,
         degass.flowrate = biofilter.max$nitrate.exchange * (co2.cbest - co2.c1) + abs(co2.remaining * 1e6 / (co2.c2 - co2.c1)) / 24 / 1000)
```

``` {r prod_degas_table}
degass.calculations %>% select(-c(feed.max, protein.max)) %>% knitr::kable( digits = 3, caption = "Table 10. **Production** facility CO~2~ management and specification.", col.names = c("System", "Tank Turnover m^3^", "Skimmer Flow m^3^", "Alkalinity kg", "NaOH Kg", "Remaining CO~2~", "Degas Flow Rate m^3^")) %>%
  kable_styling()
```

``` {r uk_degas_table}
uk.degass.calculations %>% select(-c(feed.max, protein.max)) %>% knitr::kable( digits = 3, caption = "Table 11. **UK** facility CO~2~ management and specification.", col.names = c("System", "Tank Turnover m^3^", "Skimmer Flow m^3^", "Alkalinity kg", "NaOH Kg", "Remaining CO~2~", "Degas Flow Rate m^3^")) %>%
  kable_styling()
```

***

TSS

``` {r total_system_volumes}
# calculate total system volume
total.system.volume <- tibble(system = c("breeding.juvenile", "crayling.hatching"),
                              volume = c(tank.areas$tank.volumes[1] + tank.areas$tank.volumes[4] + biofilter.max$biofilter.volume[1], tank.areas$tank.volumes[2] + tank.areas$tank.volumes[3] + biofilter.max$biofilter.volume[2]))

# calculate uk total system volume
uk.total.system.volume <- tibble(system = c("breeding.juvenile", "crayling.hatching"),
                              volume = c(uk.tank.areas$tank.volumes[1] + uk.tank.areas$tank.volumes[4] + uk.biofilter.max$biofilter.volume[1], uk.tank.areas$tank.volumes[2] + uk.tank.areas$tank.volumes[3] + uk.biofilter.max$biofilter.volume[2]))
```

```{r prod_solids}
# build solids removal component
solids.calcs <- grouped.loading %>%
  select(-c(max.mod.number, max.number)) %>%
  mutate(tss = feed.max * 0.25 -(desired.tss * biofilter.max$nitrate.exchange * 1000 / 1e6),
         required.flow = tss / (tss.te * desired.tss / 1e6) / 24 / 1000,
         discharge = tss * 30 / 1000,
         solids.evac = tss * 1e6 / (total.system.volume$volume * 1000) / feeding.period,
         drum.flow = c(tank.areas$tank.turnover[1] + tank.areas$tank.turnover[4], tank.areas$tank.turnover[2] + tank.areas$tank.turnover[3]))
```

``` {r prod_solids_table}
solids.calcs %>% select(-c(feed.max, protein.max)) %>% knitr::kable( digits = 3, caption = "Table 12. **Prod** facility solids management and specification.", col.names = c("System", "TSS Remaining", "Flow Required m^3^/h", "Discharge m^3^/day", "TSS loading mg/l", "Flow from Tanks")) %>%
  kable_styling()
```

``` {r uk_solids}
# build uk solids removal component
uk.solids.calcs <- uk.grouped.loading %>%
  select(-c(max.number, max.mod.number)) %>%
  mutate(tss = feed.max * 0.25 -(desired.tss * uk.biofilter.max$nitrate.exchange * 1000 / 1e6),
         required.flow = tss / (tss.te * desired.tss / 1e6) / 24 / 1000,
         discharge = tss * 30 / 1000,
         solids.evac = tss * 1e6 / (uk.total.system.volume$volume * 1000) / feeding.period,
         drum.flow = c(uk.tank.areas$tank.turnover[1] + uk.tank.areas$tank.turnover[4], uk.tank.areas$tank.turnover[2] + uk.tank.areas$tank.turnover[3]))
```

``` {r uk_solids_table}
uk.solids.calcs %>% select(-c(feed.max, protein.max)) %>% knitr::kable( digits = 3, caption = "Table 13. **UK** facility solids management and specification.", col.names = c("System", "TSS Remaining", "Flow Required m^3^/h", "Discharge m^3^/day", "TSS loading mg/l", "Flow from Tanks")) %>%
  kable_styling()
```


